A 3D curvilinear skeletonization algorithm with application to path tracing

### 2012-12-03 skeleton_and_pathtracing.tex
Petit ajout

Although the output of Alg.\ref{algo::3d_curvskel} may contain $2$-faces (depending on the topological properties of the input), the algorithm is said to be a \myem{curvilinear skeletonization} algorithm because it only adds $1$-faces (edges) in the inhibitor set $W$ (used for the visual aspect preservation step) (on line \ref{curvskel:01} of Alg.~\ref{algo::3d_curvskel}). For the same reason, we say that the output of Alg.~\ref{algo::3d_curvskel} is a \myem{curvilinear skeleton}.

>>>>

Although the output of Alg.\ref{algo::3d_curvskel} may contain $2$-faces, the algorithm is said to be a \myem{curvilinear skeletonization} algorithm because it only adds $1$-faces (edges) in the inhibitor set $W$ (used for the visual aspect preservation step) (on line \ref{curvskel:01} of Alg.~\ref{algo::3d_curvskel}).
For the same reason, we say that the output of Alg.~\ref{algo::3d_curvskel} is a \myem{curvilinear skeleton}. In Sec.~\ref{sec::appli_pathtrace}, the outputs of Alg.~\ref{algo::3d_curvskel} were always one dimensional complexes.
